---
title: "Shifting_tray_Markdown"
author: "Christoph Voelter"
date: "November 18, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(ggpubr)
source("C:/Users/cjv3/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/cjv3/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/cjv3/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/cjv3/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/cjv3/R/R scripts/Roger/corr_exact.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
all.data <- read.table(file="Shifting_tray_Sweetwaters_final data.txt", header=T, sep="\t")
summary(all.data)

```


##Summary



##Plotting data

###Plotting trial-to-trial effects
```{r echo=FALSE}

###Plotting side_changes
plot_individual_side <- all.data %>%
  filter(Subject != "George")%>%
  group_by(Session, side_change, Subject) %>% 
  summarize(correct_resp = mean(correct)) 


plot_ind_S1_side <- plot_individual_side %>% 
  filter(Session == 1 & side_change!="")%>%
  add_count(correct_resp)

plot_ind_S1_side_mean <- plot_ind_S1_side %>% 
  group_by(side_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p1 <- ggplot(
  data=plot_ind_S1_side, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S1_side$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("Session 1")+
  geom_segment(aes(y = plot_ind_S1_side_mean$mean_correct[1], yend = plot_ind_S1_side_mean$mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S1_side_mean$mean_correct[2], yend = plot_ind_S1_side_mean$mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = side_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 


plot_ind_S2_side <- plot_individual_side %>% 
  filter(Session == 2 & side_change!="")%>%
  add_count(correct_resp)

plot_ind_S2_side_mean <- plot_ind_S2_side %>% 
  group_by(side_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p2 <- ggplot(
  data=plot_ind_S2_side, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S2_side$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
 # scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("Session 2")+
  geom_segment(aes(y = plot_ind_S2_side_mean$mean_correct[1], yend = plot_ind_S2_side_mean$mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S2_side_mean$mean_correct[2], yend = plot_ind_S2_side_mean$mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = side_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 

###plotting box changes
plot_individual_box <- all.data %>%
  filter(Subject != "George")%>%
  group_by(Session, box_change, Subject) %>% 
  summarize(correct_resp = mean(correct)) 

plot_ind_S1_box <- plot_individual_box %>% 
  filter(Session == 1 & box_change!="")%>%
  add_count(correct_resp)

plot_ind_S1_box_mean <- plot_ind_S1_box %>% 
  group_by(box_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p3 <- ggplot(
  data=plot_ind_S1_box , aes(box_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S1_box $n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Box Change",y="Mean correct")+
  theme_few()+
 # scale_y_continuous(breaks=seq(0,1,0.25))+
  geom_segment(aes(y = plot_ind_S1_box_mean $mean_correct[1], yend = plot_ind_S1_box_mean $mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S1_box_mean$mean_correct[2], yend = plot_ind_S1_box_mean $mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = box_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 




plot_ind_S2_box  <- plot_individual_box %>% 
  filter(Session == 2 & box_change!="")%>%
  add_count(correct_resp)

plot_ind_S2_box_mean <- plot_ind_S2_box %>% 
  group_by(box_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p4 <- ggplot(
  data=plot_ind_S2_box , aes(box_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_S2_box $n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Box Change",y="Mean correct")+
  theme_few()+
 # scale_y_continuous(breaks=seq(0,1,0.25))+
  geom_segment(aes(y = plot_ind_S2_box_mean $mean_correct[1], yend = plot_ind_S2_box_mean $mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_S2_box_mean$mean_correct[2], yend = plot_ind_S2_box_mean $mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = box_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")
 

grid.arrange(p1, p2,p3,p4, nrow = 2)
 #g <- arrangeGrob(p1, p2,p3,p4, nrow = 2)
#ggsave("tray_shifting_trial effects.jpeg",g, width = 10, height = 7)



```


##t-tests

###Side changes  

```{r echo=FALSE}
tt<-t.test( plot_ind_S1_side[plot_ind_S1_side$side_change=="no",]$correct_resp, plot_ind_S1_side[plot_ind_S1_side$side_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 1: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 


```{r echo=FALSE}
tt<-t.test( plot_ind_S2_side[plot_ind_S2_side$side_change=="no",]$correct_resp, plot_ind_S2_side[plot_ind_S2_side$side_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 2: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

###Box changes 
```{r echo=FALSE}
tt<-t.test( plot_ind_S1_box[plot_ind_S1_box$box_change=="no",]$correct_resp, plot_ind_S1_box[plot_ind_S1_box$box_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 1: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test( plot_ind_S2_box[plot_ind_S2_box$box_change=="no",]$correct_resp, plot_ind_S2_box[plot_ind_S2_box$box_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")
```
* Session 2: Mean difference = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

###Comparison to chance
* Chance value: 0.5  

```{r echo=FALSE}
plot_individual <- all.data %>%
  group_by(Session, Subject) %>% 
  summarize(correct_resp = mean(correct)) 
tt<-t.test( plot_individual[plot_individual$Session==1,]$correct_resp, mu=0.5, alternative = "two.sided")
```
* Session 1: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

```{r echo=FALSE}
tt<-t.test( plot_individual[plot_individual$Session==2,]$correct_resp, mu=0.5, alternative = "two.sided")
```
* Session 2: Mean = `r round(tt$estimate, 2)`, 95% CI [`r round(tt$conf.int[1],2)`, `r round(tt$conf.int[2],2)`], *t*(`r tt$parameter`)=`r round(tt$statistic,2)`, *p*=`r round(tt$p.value,3)` 

###Plotting box preferences
```{r include=FALSE}



plot_individual_distractor1 <- all.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 1)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/24)
  

p1<-ggplot(plot_individual_distractor1, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
   ylim(0,8)+
   xlim(0,1)+
   labs(x="",y="Count of distractor choices per subject")+
   theme_few()+
   theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 1")

plot_individual_distractor2 <- all.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 2)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/24)

p2<-ggplot(plot_individual_distractor2, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
   ylim(0,8)+
   xlim(0,1)+
   labs(x="",y="Count of distractor choices per subject")+
   theme_few()+
   theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 2")


grid.arrange(p1, p2, nrow = 1)




```

```{r warning=FALSE, echo=FALSE}



plot_individual_distractor1 <- all.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 1)%>%
  filter(trial_number < 13)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)
  

p1<-ggplot(plot_individual_distractor1, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
   ylim(0,11)+
   xlim(0,1)+
   labs(x="",y="Distractor choices")+
   theme_few()+
   #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  theme(legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 1 - first half")

plot_individual_distractor2 <- all.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 1)%>%
  filter(trial_number > 12)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)

p2<-ggplot(plot_individual_distractor2, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
  scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
   ylim(0,11)+
   xlim(0,1)+
   labs(x="",y="Distractor choices")+
   theme_few()+
   #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  theme(legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 1 - second half")

plot_individual_distractor3 <- all.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 2)%>%
  filter(trial_number < 13)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)
  

p3<-ggplot(plot_individual_distractor3, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
  scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
   ylim(0,11)+
   xlim(0,1)+
   labs(x="",y="Distractor choices")+
   theme_few()+
   #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  theme(legend.position="none")+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 2 - first half")

plot_individual_distractor4 <- all.data %>%
  filter(Subject != "George" & Subject != "Saidia" & Subject != "Safari" )%>%
  filter(Session == 2)%>%
  filter(trial_number > 12)%>%
  group_by(chosen_distractor, Subject) %>% 
  count(chosen_distractor) %>%
  mutate(n = n/12)

p4<-ggplot(plot_individual_distractor4, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
    scale_color_brewer(palette="Dark2")+
    scale_fill_brewer(palette="Dark2")+
    ylim(0,11)+
    xlim(0,1)+
    labs(x="",y="Distractor choices")+
    theme_few()+
    #theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
    theme(legend.position="none")+
    #scale_y_continuous(breaks=seq(0,1,0.25))+
   ggtitle("Session 2 - second half")
 


p5<-ggplot(plot_individual_distractor4, aes(x=n, fill=chosen_distractor)) +
    geom_histogram(binwidth=0.05, alpha=.5, position="identity")+
scale_color_brewer(palette="Dark2")+
  scale_fill_brewer(palette="Dark2")+
  theme(legend.position="top")

#grid.arrange(p1, p2,p3,p4, nrow = 2)


legend <- get_legend(p5)
# 3. Remove the legend from the box plot
grid.arrange(p1, p2,p3,p4,legend, ncol=2, nrow = 3, 
             layout_matrix = rbind(c(1,2),c(3,4), c(5,5)),
             widths = c(2.7, 2.7), heights = c(2.5, 2.5,0.2))




```

