---
title: "Shifting_tray_Markdown"
author: "Christoph Voelter"
date: "November 18, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
source("C:/Users/cjv3/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/cjv3/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/cjv3/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/cjv3/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/cjv3/R/R scripts/Roger/corr_exact.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
all.data <- read.table(file="Shifting_tray_Sweetwaters_final data.txt", header=T, sep="\t")

```


##Summary



##Plotting data

###Plotting box_changes
```{r error=FALSE}

###Plotting side_changes
plot_individual <- all.data %>%
  group_by(Session, side_change, Subject) %>% 
  summarize(correct_resp = mean(correct)) 


plot_ind1 <- plot_individual %>% 
  filter(Session == 1 & side_change!="")%>%
  add_count(correct_resp)

plot_ind1_mean <- plot_ind1 %>% 
  group_by(side_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p1 <- ggplot(
  data=plot_ind1, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind1$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
  scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("Session 1")+
  geom_segment(aes(y = plot_ind1_mean$mean_correct[1], yend = plot_ind1_mean$mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind1_mean$mean_correct[2], yend = plot_ind1_mean$mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))



plot_ind2 <- plot_individual %>% 
  filter(Session == 2 & side_change!="")%>%
  add_count(correct_resp)
p2 <- ggplot(
  data=plot_ind2, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind2$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
  scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("Session 2")

###plotting box changes
plot_individual <- all.data %>%
  group_by(Session, box_change, Subject) %>% 
  summarize(correct_resp = mean(correct)) 


plot_ind1 <- plot_individual %>% 
  filter(Session == 1 & box_change!="")%>%
  add_count(correct_resp)
p3 <- ggplot(
  data=plot_ind1, aes(box_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind1$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Box Change",y="Mean correct")+
  theme_few()+
  scale_y_continuous(breaks=seq(0,1,0.25))




plot_ind2 <- plot_individual %>% 
  filter(Session == 2 & box_change!="")%>%
  add_count(correct_resp)
p4 <- ggplot(
  data=plot_ind2, aes(box_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind2$n, colour = "purple") +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Box Change",y="Mean correct")+
  theme_few()+
  scale_y_continuous(breaks=seq(0,1,0.25))

grid.arrange(p1, p2,p3,p4, nrow = 2)



```



\pagebreak  

##Paired-sample t-test
```{r}

contr_data <- plot_individual %>%  
  filter(condition == "control")

exp_data <- plot_individual %>%  
  filter(condition == "test")


t.test(exp_data$correct_resp, contr_data$correct_resp, paired = TRUE, alternative = "two.sided")
```

## GLMM

``` {r mixed modeling, error=TRUE}

# centering variables for modeling
model.data <- all.data %>% 
  mutate(z.trial = scale(trial, scale = T, center = T),
         condition = relevel(condition, ref = "control"))

## code to run the model
mm.1 <- glmer(both_ropes ~ condition + z.trial + 
               (1 + condition + z.trial |chimp)
             , data = model.data
             , family = binomial
             #, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

## save model output
#saveRDS(mm.1, "multpos_model.rds")
#save.image("mm1_mult_poss.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R}		
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=F)
#saveRDS(mm.1, "multpos_model.rds")
round(boot.res,3)
```

####Null model	 
```{r}	 
mm.1.null <- glmer(both_ropes ~ 1 + 
               (1 + condition + z.trial |chimp)
             , data = model.data
             , family = binomial
            # , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm.1, mm.1.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.1)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.1, test="Chisq")
round(xdrop1,3)
```


#### check for colinearity in the previous model.

```{R echo=FALSE}
library (car)

col.mm1 <- glm(both_ropes ~ condition + z.trial 
             , data = model.data
             , family = binomial
)
vif(col.mm1)
#no problem
```
-> no collinearity

####Model output
`````` {r plot mixed modeling, error=TRUE}

plot_model(mm.1, type='est') 
plot_model(mm.1, type='re') 
```





