---
title: "Stop Signal_Markdown"
author: "Christoph Voelter"
date: "December 02, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(ggpubr)
library(trimr)
source("C:/Users/voelterc/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/voelterc/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/voelterc/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/voelterc/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/voelterc/R/R scripts/Roger/corr_exact.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
all.data <- read.table(file="data/20200126_StopSignal_final.txt", header=T, sep="\t") %>%
  filter(Subject != "Julia") %>% #did not complete test trials
  mutate(first_move_correct = recode(first_move_correct, 'c' = 1, 'i' = 0))

#filter(Change_latency_value < 3001 & Change_latency_value > 100)%>%
  #filter(X_firsttest_trial_number != 1)

```


## Notes
### Uganda: 
* One trial excluded due to apparatus malfunction (Sarah, test trial). 
* Start position latency: Ten further test trials excluded due to data recording errors. In total, 11/ 305 test trials were removed (3.6%). 
* Change latency: One further test trial excluded due to data recording errors. In total, 2 /305 test trials were removed(0.7%).
* Change position: Ten further test trials excluded due to data recording errors. In total, 11/ 305 test trials were removed (3.6%).
* Training trials: 8 / 1183 (0.7 %) excluded duto data recording errors

### Kenya 
* Start position latency: Five test trials excluded due to data recording errors. In total, 5/ 322 test trials were removed (1.6%). 
* Change latency: Two test trial excluded due to data recording errors. In total, 2 /322 test trials were removed(0.6%).
* Change position: Zero test trials excluded due to data recording errors. 
* Training trials: 11 / 1306 (0.8 %) excluded duto data recording errors


##Summary



##Plotting data

###Plotting trial to trial effects
```{r error=FALSE}

###Plotting side_changes
plot_individual_side <- all.data %>%
  filter(side_change!="") %>%
  filter(!is.na(first_move_correct)) %>%
  group_by(condition, side_change, Subject) %>% 
  summarize(correct_resp = mean(first_move_correct)) 


plot_ind_training_side <- plot_individual_side %>% 
  filter(condition == "training") %>%
  add_count(correct_resp)

plot_ind_training_side_mean <- plot_ind_training_side %>% 
  group_by(side_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p1 <- ggplot(
  data=plot_ind_training_side, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_training_side$n, colour = "blue", alpha=0.1 ) +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("training")+
  geom_segment(aes(y = plot_ind_training_side_mean$mean_correct[1], yend = plot_ind_training_side_mean$mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_training_side_mean$mean_correct[2], yend = plot_ind_training_side_mean$mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = side_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")



plot_ind_test_side <- plot_individual_side %>% 
  filter(condition == "test") %>%
  add_count(correct_resp)

plot_ind_test_side_mean <- plot_ind_test_side %>% 
  group_by(side_change) %>% 
  summarize(mean_correct = mean(correct_resp)) 

p2 <- ggplot(
  data=plot_ind_test_side, aes(side_change, correct_resp, group = Subject)) +   
  geom_point(size = plot_ind_test_side$n, colour = "blue", alpha=0.05 ) +
  geom_line(lty=2)+
  ylim(0,1)+
  labs(x="Side Change",y="Mean correct")+
  theme_few()+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("test")+
  geom_segment(aes(y = plot_ind_test_side_mean$mean_correct[1], yend = plot_ind_test_side_mean$mean_correct[1], x = 1 -0.2, xend = 1 + 0.2))+
  geom_segment(aes(y = plot_ind_test_side_mean$mean_correct[2], yend = plot_ind_test_side_mean$mean_correct[2], x = 2 -0.2, xend = 2 + 0.2))+
  stat_compare_means(aes(group = side_change), paired = TRUE, method="t.test", label.x = 1.3)#, label = "p.signif")


grid.arrange(p1, p2, nrow = 1)
 g <- arrangeGrob(p1, p2, nrow = 1)
ggsave("stopsignal_trial to trial_correct.jpeg",g, width = 10, height = 6)



```



\pagebreak  

##Paired-sample t-test
```{r}


t.test( plot_ind_training_side[plot_ind_training_side$side_change=="no",]$correct_resp, plot_ind_training_side[plot_ind_training_side$side_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")


t.test( plot_ind_test_side[plot_ind_test_side$side_change=="no",]$correct_resp, plot_ind_test_side[plot_ind_test_side$side_change=="yes",]$correct_resp, paired = TRUE, alternative = "two.sided")

t.test( plot_ind_training_side[plot_ind_training_side$side_change=="no",]$correct_resp, mu=0.5, alternative = "two.sided")
t.test( plot_ind_training_side[plot_ind_training_side$side_change=="yes",]$correct_resp, mu=0.5, alternative = "two.sided")

t.test( plot_ind_test_side[plot_ind_test_side$side_change=="no",]$correct_resp, mu=0.5, alternative = "two.sided")
t.test( plot_ind_test_side[plot_ind_test_side$side_change=="yes",]$correct_resp, mu=0.5, alternative = "two.sided")




```



##Test trials: latencies

```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
test.data <- read.table(file="data/20200126_StopSignal_final.txt", header=T, sep="\t") %>%
  filter(Subject != "Julia") %>% #did not complete test trials
  filter(condition=="test") %>%
  filter(firsttest_trial_number != 1) %>%
  mutate(first_move_correct = recode(first_move_correct, 'c' = 1, 'i' = 0)) %>%
  filter(Change_latency_value > 100) 
  
```

```{r remove outliers, include=FALSE}
test.data2 <- test.data %>%
  mutate(participant = Subject) %>%
  mutate(rt = Change_latency_value) %>%
  mutate(accuracy = first_move_correct) %>%
  mutate(accuracy = recode(accuracy, 'c' = 1, 'i' = 0))
  
trimmed.test.data <- sdTrim(data = test.data2, minRT = 150, sd = 2, 
                      perCondition = FALSE, perParticipant = TRUE, 
                      returnType = "mean", digits = 0)

plot_individual2 <- test.data %>%
  filter(!is.na(Change_latency_value)) %>%
  group_by(Subject) %>% 
  summarize(change_latency = mean(Change_latency_value))

trimmed.test.data <- trimmed.test.data %>%
  mutate(Subject=plot_individual2$Subject)

 plot_individual3 <- test.data %>%
  filter(!is.na(Change_position_value)) %>%
  group_by(Subject) %>% 
  summarize(Change_position = mean(Change_position_value))


plot_individual_trimmed <- plot_individual2 %>% 
  inner_join(trimmed.test.data )%>%
  inner_join(plot_individual3 )%>%  
  mutate(trimmed_change_latency=test)%>%
  add_count(trimmed_change_latency) %>%
  select(-participant, -test)%>%
  rename(n_lat=n)%>%
  add_count(Change_position) %>%
  rename(n_pos=n)



```




```{r}  
  ###Plotting change latency


p1 <- 
  ggplot(
  data=plot_individual_trimmed , aes(x=rep(1, 52), y=trimmed_change_latency))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(size = plot_individual_trimmed$n_lat, colour = "blue", alpha=0.1 ) +
  geom_line(lty=2)+
  ylim(0,5000)+
  xlim(0,2)+
  labs(x="",y="Change latency")+
  theme_few()+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("change latency")

p2 <- 
  ggplot(
  data=plot_individual_trimmed , aes(x=rep(1, 52), y=Change_position))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(size = plot_individual_trimmed$n_pos, colour = "blue", alpha=0.1 ) +
  geom_line(lty=2)+
  ylim(0,22)+
  xlim(0,2)+
  labs(x="",y="Change position")+
  theme_few()+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("change position")


grid.arrange(p1, p2, nrow = 1)
 g <- arrangeGrob(p1, p2, nrow = 1)
ggsave("graphics/stopsignal_test trials.jpeg",g, width = 10, height = 6)
```



```{r}
  ggplot(
  data=plot_individual_trimmed , aes(x=age, y=trimmed_change_latency))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(size = plot_individual_trimmed$n_lat, colour = "blue", alpha=0.1 ) +
  geom_line(lty=2)+
  ylim(0,5000)+
  xlim(0,2)+
  labs(x="",y="Change latency")+
  theme_few()+
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())+
  #scale_y_continuous(breaks=seq(0,1,0.25))+
  ggtitle("change latency")


```





